%%% Summaries of documents: 
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin = 2cm}
\newcommand{\enter}{\vspace{0.5cm}}
\begin{document}
	
	\section{Afshar, Sepideh (2015) Modelling and infrared thermal imagery of hot particle curtains. PhD thesis, James Cook University.}
	
	\subsection{Quotable}
	
		\subsubsection{Introduction}
			\begin{itemize}
				\item Particle curtains are defined as a stream of particles falling a fixed distance through a gas or fluid
				phase. 
				\item They are very common in industrial drying, particularly in the minerals and food industry.
				\item Typical unit operations in drying
				industry are fluidised beds, spray dryers, flighted rotary dryers (FRD) and solid particle receivers
				(SPR).
				\item Flighted rotary dryers are used widely in industry because of their simplicity and their
				ability to handle very large throughputs.
				\item Particle curtains are important in flighted rotary dryers.
				\item Researchers have found that the properties of the individual particles, such as particle
				temperature and particle size, and the operational characteristics such as flow rates and curtain
				depth, solid volume fraction and rates of heat transfer are important in characterising the behaviour
				of particle curtains.
				\item CFD has applied successfully to model
				5particle curtains in isothermal conditions; however, there are relatively few CFD studies of hot
				particle curtains. Furthermore, the use of CFD to approximate bulk curtain behaviour has not been
				described.
				\item There are a few examples of the use of image analysis to characterise particle curtains.
				These have shown promise and suggest that infrared thermal imagery might provide good data for
				characterising the thermal properties of particle curtains. However, there are no examples of this
				application to two-phase systems. This illustrates a gap in our understanding.
			\end{itemize}
		 
		
		
	
	\subsection{General Ideas}
	
		\subsubsection{Introduction}
			\begin{itemize}
				\item Drying is governed by two-phase heat and mass transfer processes.
				\item Characterising the interaction between gas and particles has spurred the interest of researchers for
				decades.
				\item Despite the importance of particle curtains in flighted rotary dryers, a
				comprehensive model that describes the influence of these properties has yet to be developed.
				\item There are a few examples of the use of image analysis to characterise particle curtains.
			\end{itemize}


\section{Andrew LEE, (2008) Modelling the Solids Transport Phenomena Within Flighted Rotary Dryers. PhD Thesis, James Cook University}

	\subsection{Quotable}
	
	\subsubsection{Introduction}
	\begin{itemize}
		\item ... 
	\end{itemize}
	
	
	
	
	\subsection{General Ideas}
	
	\subsubsection{Introduction}
	\begin{itemize}
		\item ... 
	\end{itemize}



\end{document}

